Improved Approximation Algorithms for the Maximum Carpool Matching Problem

### 2017-02-05 src/abstract.tex
fix

We show that the \carpool can be formulated as an unconstrained
submodular maximization problem, thus it admits a
$\frac{1}{2}$-approximation algorithm.
We show that the same formulation does not hold for the \gcp,
nevertheless, we present a $\frac{1}{2} - \varepsilon$-approximation algorithm
for the \gcp as well.
For the unweighted variant of
the problems when the maximum possible capacity, $C$, is fixed, we give
a $(\frac{C + 1}{2C} - \varepsilon)$-approximation algorithm.
We also show that the problem remains APX-hard even if $C \leq 3$.

>>>>

We show that the \carpool can be formulated as an unconstrained
submodular maximization problem, thus it admits a
$\frac{1}{2}$-approximation algorithm.
We show that the same formulation does not hold for the \gcp,
nevertheless, we present a $\frac{1}{2} - \varepsilon$-approximation algorithm
for the \gcp as well.
For the unweighted variant of
the problems when the maximum possible capacity, $\cmax$, is fixed, we give
a $(\frac{\cmax + 1}{2\cmax} - \varepsilon)$-approximation algorithm.
We also show that the problem remains APX-hard even if $\cmax \leq 3$.

### 2017-02-05 src/intro.tex
fix

\begin{figure}
\centering
\input{fig-carpool}
\caption[]{
\label{fig:carpool}
A carpool matching example: 
\subref{carpool:input}
a directed graph with capacities on the vertices and weights on the arcs. 
\subref{carpool:output}
a feasible matching with total weight of 26.
$P$ is the set of blue vertices, and $D$ is the set of red, dashed vertices. 
}
\end{figure}

@@

For the general set packing problem, the best known approximation algorithm is
due to Chandra et al.~\cite{chandra2001greedy} and it admits a 
$\frac{2(k +1)}{3}$ approximation ratio where $k$ is the size of the sets.

@@

In Section~\ref{sec:local} we consider the unweighted variant of the
problem.  We provide a $(\frac{2\cmax}{\cmax+1} + \eps)$-approximation
algorithm, for any $\eps>0$, where $\cmax$ is the maximum capacity.
We also show that \carpool is APX-hard even if $\cmax \leq 3$.
%
In Section~\ref{sec:group} we consider \gcp.  
We first show that the unconstrained submodular maximization formulation for
the \carpool does not follow for the \gcp.
We show, however, that this problem still admits
a $(\frac{1}{2} -\varepsilon)$-approximation algorithm, and argue that the local
search algorithm generalizes to \gcp as well.

>>>>

\begin{figure}
\centering
\input{fig-carpool}
\caption[]{
\label{fig:carpool}
A carpool matching example: 
\subref{carpool:input}
a directed graph with capacities on the vertices and weights on the arcs. 
\subref{carpool:output}
a feasible matching with total weight of 23.
$P_M$ is the set of blue vertices, and $D_M$ is the set of red, dashed
vertices, and $Z_M$ contains only the dotted, black vertex.
}
\end{figure}

@@

For the general set packing problem, the best known approximation algorithm is
due to Chandra et al.~\cite{chandra2001greedy} and it admits a 
$\frac{3}{2(k +1)}$ approximation ratio where $k$ is the size of the sets.

@@

In Section~\ref{sec:local} we consider the unweighted variant of the
problem.  We provide a $(\frac{\cmax+1}{2\cmax} + \eps)$-approximation
algorithm, for any $\eps>0$, where $\cmax$ is the maximum capacity.
We also show that \carpool is APX-hard even if $\cmax \leq 3$.
%
In Section~\ref{sec:group} we consider \gcp.  
We first show that the unconstrained submodular maximization formulation for
the \carpool does not follow for the \gcp.
We show, however, that this problem still admits
a $(\frac{1}{2} -\varepsilon)$-approximation algorithm, and argue that the local
search algorithm generalizes to \gcp as well.
